---
title: "Suicidal Behaviors Among Adolescents"
author: "Nina Austria, Raian Rith"
date: "11/01/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Installing Libraries:

Installing all necessary libraries.

```{r}
library(tidyverse)
library(readr)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(naniar)
library(forcats)
library(wordcloud)
library(tm)
library(SnowballC)
library(RColorBrewer)
library(tidytext)
```

## Used head function to look at top 6 rows of data and read the data in.

We read the data in and then look at the first few rows of code. 

```{r}
sb <- read_csv("GHSH.csv")
```

# Summarize the Data

We use the glimpse and summary functions to look at the summary of the data. 

```{r}
glimpse(sb)
```

```{r}
summary(sb)
```

# Data Cleaning

Check for and drop any missing values:

```{r}
sum(is.na(sb)) # 6 missing values
sb <- drop_na(sb)
```

Rename 'Age Group' variable so that there is no whitespace:

```{r}
sb <- rename(sb, Age_Group = 'Age Group')
```

Average number of attempted suicides by country (there are 26 countries in the dataset):

```{r}
sb %>% group_by(Country) %>% summarize(mean_attempted_suicides = mean(Attempted_suicide)) %>% arrange(desc(mean_attempted_suicides))
```

Average number of attempted suicides by year (years range from 2010-2017):

```{r}
sb %>% group_by(Year) %>% summarize(mean_attempted_suicides = mean(Attempted_suicide)) %>% arrange(desc(mean_attempted_suicides))
```

Average number of attempted suicides by age group (13-15 VS 16-17):

```{r}
sb %>% group_by(Age_Group) %>% summarize(mean_attempted_suicides = mean(Attempted_suicide)) %>% arrange(desc(mean_attempted_suicides))
```

Average number of attempted suicides by sex:

```{r}
sb %>% group_by(Sex) %>% summarize(mean_attempted_suicides = mean(Attempted_suicide)) %>% arrange(desc(mean_attempted_suicides))
```

# Data Visualization

Scatterplot of attempted suicide VS number of close friends: (not sure if this makes sense.. what exactly is attempted suicide var?)

```{r}
ggplot(sb, mapping = aes(x=No_close_friends, y = Attempted_suicide)) +
geom_point(color = "black") +
labs(title="Number of close friends VS number of attempted suicides")
```
